A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
Updates

\begin{figure*}[!tb]\centering\includegraphics[width=\linewidth]
  {corpus.pdf}\caption{Corpus}\label{fig:corpus}
\end{figure*}

@@

We now describe the corpus used in this study.

@@

\subsection{CRAN Packages}

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and
should have better code coverage. The resulting set has
\summary{CorpusRevdeps}\footnote{Such triples represent ($min$ / $mean$ /
  $max$)} reverse dependencies and consists of \CorpusRCodeRnd lines of R code
and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran)\footnote{Excluding comments and blank lines using \url{github.com/AlDanial/cloc}}.
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means.
Packages with over \CorpusEvalsPackageTreshold eval call sites are annotated.

>>>>

This section describes the infrastructure we used to run the dynamic program
analysis to record the calls to evals.

\begin{figure*}[!tb]\centering\includegraphics[width=\linewidth]
  {pipeline.pdf}\caption{Pipeline}\label{fig:pipeline}
\end{figure*}

@@

The corpus for this study includes R programs extracted from popular R packages
as well as complete user-written data-analysis scripts. In this section we
describe the methodology used to collect them.

\subsection{CRAN Packages}\label{sec:corpus}

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and have
better code coverage and therefore more code to run. The resulting set has
\summary{CorpusRevdeps}\footnote{Such triples represent ($min$ / $mean$ /
  $max$)} reverse dependencies and consists of \CorpusRCodeRnd lines of R code
and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran)\footnote{Excluding
  comments and blank lines using \url{github.com/AlDanial/cloc}}.
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means.
Packages with over \CorpusEvalsPackageTreshold eval call sites are annotated.

@@
